---
title: "PaperCode"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load required packages and sources

```{r library, message=F}
library(ggplot2)
library(randomForest)
library(caret)
library(Rtsne)
library(dplyr)
library(ggsci)
library(tidyr)
library(foreach)
library(doParallel)
source("grid_arrange_share_legend.R")
source("kFoldCV_BaseLearner.R")
source("kFoldCV_GoldStandard.R")
source("theme_self.R")
source("modelFit.R")
```

## MAIN: Prepare data for analyzing

```{r prepare_data}
labels <- core[, c("RPT", "LKADT_P", "DEATH", "DISCONT", "ENDTRS_C", "ENTRT_PC")]
labels$DISCONT <- as.integer(labels$DISCONT)
labels$ENTRT_PC <- as.integer(labels$ENTRT_PC)
labels <- na.omit(labels)

# construct new labels
labels$new_Death <- ifelse(labels$DEATH == 'YES' & labels$LKADT_P <= 96, 1, 0)
labels$new_Discont <- ifelse(grepl("AE", labels$ENDTRS_C) & labels$ENTRT_PC <= 93, 1, 0)
labels$new_label <- ifelse(labels$new_Death == 0 & labels$new_Discont == 0 & labels$DISCONT == 0, 0, 1)

death <- core[, c("RPT", "DEATH")]
death$DEATH <- vapply(death$DEATH, function(x) ifelse(x == "YES", 1, 0), numeric(1))

coreData <- cbind(labels[, c("RPT", "new_label")], 
                  DEATH = death[death$RPT %in% labels$RPT, "DEATH"],
                  DEATH_day = core[core$RPT %in% labels$RPT, "LKADT_P"],
                  DISCONT = core[core$RPT %in% labels$RPT, "DISCONT"],
                  DISCONT_day = core[core$RPT %in% labels$RPT, "ENTRT_PC"],
                  core_habini[core_habini$RPT %in% labels$RPT, -1],
                  core_exclude[core_exclude$RPT %in% labels$RPT, -1])
coreData_Normal <- coreData
coreData_Normal[, c(7:84)] <- lapply(coreData_Normal[, c(7:84)], function(x) (x-min(x))/(max(x)-min(x)))

ASC <- coreData[grepl("^ASC", coreData$RPT), ]
CEL <- coreData[grepl("^CEL", coreData$RPT), ]
VEN <- coreData[grepl("^VEN", coreData$RPT), ]

ASC_Normal <- coreData_Normal[grepl("^ASC", coreData_Normal$RPT), ]
CEL_Normal <- coreData_Normal[grepl("^CEL", coreData_Normal$RPT), ]
VEN_Normal <- coreData_Normal[grepl("^VEN", coreData_Normal$RPT), ]
```

## MAIN: Summary data: table 1

```{r Table1}
core <- read.csv("data/CoreTable_training.csv", header = T, stringsAsFactors = F)
coreSummary <- core[, c("STUDYID", "LKADT_P", "DEATH", "DISCONT", "ENDTRS_C", "ENTRT_PC", "AGEGRP")]
coreSummary$DEATH <- ifelse(coreSummary$DEATH == 'YES', 1, 0)
coreSummary$DISCONT <- as.numeric(coreSummary$DISCONT)
coreSummary$ENTRT_PC <- as.numeric(coreSummary$ENTRT_PC)
coreSummary$AGEGRP <- as.numeric(coreSummary$AGEGRP)
coreSummary$AGEGRP[is.na(coreSummary$AGEGRP)] <- 85
summaryCore <- tibble::as.tibble(coreSummary) %>%
  group_by(STUDYID) %>%
  summarise(Sample = n(), 
            medianAge = median(AGEGRP),
            perDiscont = sum(DISCONT, na.rm = T) / n(),
            medianDiscont = median(ENTRT_PC, na.rm = T),
            perDiscontMissing = sum(is.na(ENTRT_PC)) / n(),
            perDeath = sum(DEATH) / n(),
            medianDeath = median(LKADT_P),
            perAE = sum(ENDTRS_C == 'AE') / n(),
            perPossibleAE = sum(ENDTRS_C == 'possible_AE') / n(),
            perProgression = sum(ENDTRS_C == 'progression') / n(),
            perComplete = sum(ENDTRS_C == 'complete') / n(),
            perTrtMissing = sum(ENDTRS_C == 'misce') / n())
```

## MAIN: Base learner selection: figure 2

```{r figure2}
# will take a long time ...
cores <- makeCluster(detectCores()-1)
registerDoParallel(cores)

TotalinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_BaseLearner(coreData_Normal, 5, i)
  temp
}
ASCinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_BaseLearner(ASC_Normal, 5, i)
  temp
}
CELinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_BaseLearner(CEL_Normal, 5, i)
  temp
}
VENinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_BaseLearner(VEN_Normal, 5, i)
  temp
}

stopCluster(cores)

TotalinCohortCV_Normal$Cohort <- 'ALL'
ASCinCohortCV_Normal$Cohort <- "ASC"
CELinCohortCV_Normal$Cohort <- "CEL"
VENinCohortCV_Normal$Cohort <- "VEN"
TinCohortCV_Normal <- rbind(TotalinCohortCV_Normal, ASCinCohortCV_Normal, CELinCohortCV_Normal, VENinCohortCV_Normal)
TinCohortCV_Normal$model <- reorder(TinCohortCV_Normal$model, TinCohortCV_Normal$value)

# A, B
color <- c("White", "#D0DFE6FF", "#95CC5EFF", "#F7C530FF", "#6EE2FFFF", "#FF410DFF")
p_AUC <- ggplot(subset(TinCohortCV_Normal, curve == "AUC" & Cohort == "ALL"))
p_AUC <- p_AUC + geom_violin(aes(model, value, fill = model), alpha = 0.8, width = 0.5, draw_quantiles = 0.5) + theme_bw() + 
  theme_self() + scale_fill_manual(name = "Models", values = color) + #, labels = c("Baseline   ", "Linear Regression   ", "Logistic Regression   ", "Cox   ", "BAG-CART   ", "Random Forest   ")) + 
  labs(x = "Models", y = "Area Under ROC Curve") + scale_y_continuous(limits = c(0.2, 0.9)) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + guides(fill = guide_legend(nrow=2,byrow=TRUE)) 
p_AUPRC <- ggplot(subset(TinCohortCV_Normal, curve == "AUPRC" & Cohort == "ALL"))
p_AUPRC <- p_AUPRC + geom_violin(aes(model, value, fill = model), alpha = 0.8, width = 0.5, draw_quantiles = 0.5) + theme_bw() +
  theme_self() + scale_fill_manual(name = "Models", values = color) + #, labels = c("Baseline   ", "Linear Regression   ", "Logistic Regression   ", "Cox   ", "BAG-CART   ", "Random Forest   ")) + 
  labs(x = "Models", y = "Area Under PR Curve") + scale_y_continuous(limits = c(0, 0.6)) +
  guides(fill = guide_legend(nrow=2,byrow=TRUE)) + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
grid_arrange_share_legend(p_AUC, p_AUPRC, nrow = 1, ncol = 2, position = 'bottom')

# C, D
p_AUC <- ggplot(subset(TinCohortCV_Normal, curve == "AUC" & Cohort != "ALL"))
p_AUC <- p_AUC + geom_boxplot(aes(Cohort, value, fill = model), alpha = 0.8) + theme_bw() + 
  theme_self() + scale_fill_manual(name = "Models", values = color) + 
  labs(x = "Cohorts", y = "Area Under ROC Curve") + scale_y_continuous(limits = c(0.2, 0.9)) +
  theme(legend.position = "none")
p_AUPRC <- ggplot(subset(TinCohortCV_Normal, curve == "AUPRC" & Cohort != "ALL"))
p_AUPRC <- p_AUPRC + geom_boxplot(aes(Cohort, value, fill = model), alpha = 0.8) + theme_bw() +
  theme_self() + scale_fill_manual(name = "Models", values = color) + 
  labs(x = "Cohorts", y = "Area Under PR Curve") + scale_y_continuous(limits = c(0, 0.6)) +
  theme(legend.position = "none")
grid.arrange(p_AUC, p_AUPRC, ncol = 2)
```

## REVISION: Use some of the responsers as predictors

```{r responser_to_predictor}

coreData_addPred <- cbind(labels[, c("RPT", "new_label")], 
                  DEATH = death[death$RPT %in% labels$RPT, "DEATH"],
                  DEATH_day = core[core$RPT %in% labels$RPT, "LKADT_P"],
                  DISCONT = core[core$RPT %in% labels$RPT, "DISCONT"],
                  DISCONT_day = core[core$RPT %in% labels$RPT, "ENTRT_PC"],
                  Treatment = core[core$RPT %in% labels$RPT, "ENDTRS_C"],
                  core_habini[core_habini$RPT %in% labels$RPT, -1],
                  core_exclude[core_exclude$RPT %in% labels$RPT, -1])
coreData_addPred[, c(8:85)] <- lapply(coreData_addPred[, c(8:85)], 
                                      function(x) (x-min(x))/(max(x)-min(x)))


cores <- makeCluster(detectCores()-1)
registerDoParallel(cores)

TotalinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  set.seed(i)
  coreData_addPred <- coreData_addPred[sample(nrow(coreData_addPred)), ]
  folds <- cut(seq(1, nrow(coreData_addPred)), breaks = 5, labels = F)
  results <- data.frame()
  for (k in 1:5) {
    testIndexes <- which(folds == k, arr.ind = T)
    test <- coreData_addPred[testIndexes, ]
    train <- coreData_addPred[-testIndexes, ]
    train$DISCONT <- as.numeric(as.character(train$DISCONT))
    train$DISCONT_day <- as.numeric(as.character(train$DISCONT_day))
    train <- na.omit(train)
    test$DISCONT <- as.numeric(as.character(test$DISCONT))
    test$DISCONT_day <- as.numeric(as.character(test$DISCONT_day))
    test <- na.omit(test)
    
    train_discont <- train[, c(5, 8:85)]
    test_discont <- test[, c(5, 8:85)]
    rf_model_DISCONT <- modelFit(DISCONT ~ ., train_discont, test_discont, model = "rf", seed = 1234, target_column = "DISCONT")
    
    train_asResponser <- train[, c(5, 3:4, 6:85)]
    test_asResponser <- test[, c(5, 3:4, 6:85)]
    rf_model_DISCONT_Responsers <- modelFit(DISCONT ~ ., train_asResponser, test_asResponser, model = "rf", seed = 1234, target_column = "DISCONT")
    rf_model_NEW <- modelFit(new_label ~ ., train[, c(2, 8:85)], test[, c(5, 8:85)], model = "rf", seed = 1234, target_column = "DISCONT")
    res <- data.frame(identity = rep(c("78 Feature", "78 Feature + Responsers", "78 Feature (NEW)"), each = 2),
                      value = c(rf_model_DISCONT$roc$auc, rf_model_DISCONT$pr$auc.integral,
                                rf_model_DISCONT_Responsers$roc$auc, rf_model_DISCONT_Responsers$pr$auc.integral, 
                                rf_model_NEW$roc$auc, rf_model_NEW$pr$auc.integral),
                      stringsAsFactors = F)
    res$curve <- rep(c("AUC", "AUPRC"), 3)
    results <- rbind(results, res)
  }
  results
}

stopCluster(cores)
```

## MAIN: Gold standard selection: figure 3

```{r figure3}
# Use parallel computing to accelerate the processing
cores <- makeCluster(detectCores()-1)
registerDoParallel(cores)

# will also take a long time ... 
TotalinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(coreData_Normal, 5, i)
  temp
}
ASCinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(ASC_Normal, 5, i)
  temp
}
CELinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(CEL_Normal, 5, i)
  temp
}
VENinCohortCV_Normal <- foreach(i = 1:10, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(VEN, 5, i)
  temp
}

stopCluster(cores)

TotalinCohortCV_Normal$Cohort <- "ALL"
ASCinCohortCV_Normal$Cohort <- "ASC"
CELinCohortCV_Normal$Cohort <- "CEL"
VENinCohortCV_Normal$Cohort <- "VEN"
TinCohortCV_Normal <- rbind(TotalinCohortCV_Normal, ASCinCohortCV_Normal, CELinCohortCV_Normal, VENinCohortCV_Normal)
TinCohortCV_Normal$gold_standard <- with(TinCohortCV_Normal, reorder(gold_standard, value))

# A, B
labels_figure3 <- labels[, c("DEATH", "DISCONT", "ENDTRS_C", "ENTRT_PC", "LKADT_P")]
labels_figure3$DEATH <- ifelse(labels_figure3$DEATH == 'YES', 'YES', 'NO')
labels_figure3$risk_level <- sapply(labels_figure3$ENDTRS_C, function(x) {
  if (x == 'AE') return(1)
  if (x == 'complete') return(0)
  if (x == 'possible_AE') return(0.8)
  if (x == 'progression') return(0.5)
})
labels_figure3$ENDTRS_C <- with(labels_figure3, reorder(ENDTRS_C, risk_level))
colors <- c("#fecc5c", "#fd8d3c", "#e31a1c", "#bd0026")
p <- ggplot(labels_figure3, aes(x = ENTRT_PC, y = DISCONT))
p <- p + geom_point(aes(shape = DEATH, color = ENDTRS_C), position = "jitter") + theme_self() + scale_y_discrete(limits = c(0, 1), labels = c("  0", "  1")) + 
  scale_color_manual(values = colors, name = "Treatment\nStatus") + scale_x_continuous(limits = c(0, 310)) + geom_vline(xintercept = 93, linetype = "dashed") + 
  scale_shape_manual(values = c(16, 4), name = "Death\nStatus") + geom_text(aes(x = 46, y = 2, label = 'Early\nDiscontinuation')) + 
  labs(x = 'Treatment Days', y = 'Discontinuation Status')

labels_figure3$DEATH_status <- ifelse(labels_figure3$DEATH == 'YES' & labels$LKADT_P <= 96, 1, 0)
labels_figure3$Treatment_status <- ifelse(grepl("AE", labels_figure3$ENDTRS_C), 1, 0)
labels_figure3$new <- ifelse(labels_figure3$DEATH_status + labels_figure3$DISCONT + labels_figure3$Treatment_status, 1, 0)
p1 <- ggplot(labels_figure3, aes(x = ENTRT_PC, y = new))
p1 <- p1 + geom_point(aes(shape = DEATH, color = ENDTRS_C), position = "jitter") + theme_self() + scale_y_discrete(limits = c(0, 1), labels = c("  0", "  1")) + 
  scale_color_manual(values = colors, name = "Treatment\nStatus") + scale_x_continuous(limits = c(0, 310)) + geom_vline(xintercept = 93, linetype = "dashed") + 
  scale_shape_manual(values = c(16, 4), name = "Death\nStatus") + geom_text(aes(x = 46, y = 2, label = 'Early\nDiscontinuation')) + 
  labs(x = 'Treatment Days', y = 'New Standard')

grid_arrange_share_legend(p, p1, nrow = 1, ncol = 2, position = "bottom") # 9 x 3

# C, D
color <- c("White", "#D0DFE6FF", "#FF410DFF")
p_AUC <- ggplot(subset(TinCohortCV_Normal, curve == "AUC"))
p_AUC <- p_AUC + geom_boxplot(aes(Cohort, value, fill = gold_standard)) + theme_bw() +
  theme_self() + scale_fill_manual(name = "Predictor", values = color, labels = c("Baseline", "Discontinuation", "New standard")) + scale_x_discrete(labels = c("Full Dataset", "ASC", "CEL", "VEN")) +
  labs(x = "Cohort", y = "Area Under ROC Curve") + scale_y_continuous(limits = c(0.2, 0.9))
p_AUPRC <- ggplot(subset(TinCohortCV_Normal, curve == "AUPRC"))
p_AUPRC <- p_AUPRC + geom_boxplot(aes(Cohort, value, fill = gold_standard)) + theme_bw() +
  theme_self() + scale_fill_manual(name = "Predictor", values = color, labels = c("Baseline", "Discontinuation", "New standard")) + scale_x_discrete(labels = c("Full Dataset", "ASC", "CEL", "VEN")) + 
  labs(x = "Cohort", y = "Area Under PR Curve") + scale_y_continuous(limits = c(0, 0.6))
grid_arrange_share_legend(p_AUC, p_AUPRC, nrow = 1, ncol = 2, position = "bottom")
```

## REVISION: Gold standard selection: test

```{r gs_test}
cores <- makeCluster(detectCores()-1)
registerDoParallel(cores)

TotalinCohortCV_Normal_GS <- foreach(i = 1:60, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(coreData_Normal, 5, i)
  temp
}
ASCinCohortCV_Normal_GS <- foreach(i = 1:60, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(ASC_Normal, 5, i)
  temp
}
CELinCohortCV_Normal_GS <- foreach(i = 1:60, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(CEL_Normal, 5, i)
  temp
}
VENinCohortCV_Normal_GS <- foreach(i = 1:60, .combine = rbind) %dopar% {
  temp <- kFoldCV_GoldStandard(VEN_Normal, 5, i)
  temp
}

stopCluster(cores)

discont_score <- subset(VENinCohortCV_Normal_GS, gold_standard == "discont" & curve == "AUC")
new_score <- subset(VENinCohortCV_Normal_GS, gold_standard == "new" & curve == "AUC")
wilcox.test(discont_score$value, new_score$value)

discont_score <- subset(VENinCohortCV_Normal_GS, gold_standard == "discont" & curve == "AUPRC")
new_score <- subset(VENinCohortCV_Normal_GS, gold_standard == "new" & curve == "AUPRC")
wilcox.test(discont_score$value, new_score$value)
```

## MAIN: Feature importance: figure 4

```{r figure4}
cores <- makeCluster(detectCores()-1)
registerDoParallel(cores)

# this will take extremely long time ...
control <- trainControl(method = "repeatedcv", number = 5, repeats = 10)
model <- train(new_label ~ ., data = coreData_Normal[, c(2, 7:84)], method = "rf", trControl = control, importance = TRUE)
importance <- varImp(model, scale = F)
#-----------------------------------------------------#
# Then we label the features with categories by hand..#
#-----------------------------------------------------#
Importance <- read.csv("data/importance.csv")
colnames(Importance)[1] <- "Features"

model_ASC <- train(new_label ~ ., data = coreData_Normal[grep("^ASC|^CEL", coreData_Normal$RPT), c(2, 7:84)], method = "rf", trControl = control, importance = TRUE)
model_CEL <- train(new_label ~ ., data = coreData_Normal[grep("^CEL|^VEN", coreData_Normal$RPT), c(2, 7:84)], method = "rf", trControl = control, importance = TRUE)
model_VEN <- train(new_label ~ ., data = coreData_Normal[grep("^VEN|^ASC", coreData_Normal$RPT), c(2, 7:84)], method = "rf", trControl = control, importance = TRUE)

stopCluster(cores)

importance_ASC <- varImp(model_ASC, scale = F)
importance_CEL <- varImp(model_CEL, scale = F)
importance_VEN <- varImp(model_VEN, scale = F)

Importance_ASC <- importance_ASC$importance
Importance_CEL <- importance_CEL$importance
Importance_VEN <- importance_VEN$importance
Importance_ASC$Category <- Importance$Category
Importance_CEL$Category <- Importance$Category
Importance_VEN$Category <- Importance$Category

# A
Importance$Features <- with(Importance, reorder(Features, Overall))
p_Importance <- ggplot(Importance[Importance$Overall > 0, ], aes(x = Features, y = Overall, fill = Category)) + 
  geom_bar(width = 0.5, stat = "identity") + coord_flip() + theme_self() + 
  labs(x = "Features", y = "Importance") + 
  theme(legend.title = element_blank(), legend.position = c(0.68, 0.06),
        legend.box.background = element_blank(), legend.key.size = unit(0.4, "cm")) + 
  scale_fill_manual(values = c("#4DBBD5FF", "#E64B35FF", "#00A087FF", "#3C5488FF", "#F39B7FFF"))

# A subplot
p_Importance_sub <- ggplot(Importance[Importance$Overall > 0, ], aes(x = Category, y = Overall, fill = Category)) + 
  geom_boxplot(width = 0.5) + coord_flip() + theme_self() + 
  labs(x = "Categories", y = "Importance") + 
  theme(axis.text.y = element_blank(), legend.position = "none", axis.ticks.y = element_blank()) + 
  scale_fill_manual(values=c("#4DBBD5FF", "#E64B35FF", "#00A087FF", "#3C5488FF", "#F39B7FFF"))

# B, C, D
Importance_ASC$Features <- row.names(Importance_ASC)
Importance_ASC <- Importance_ASC[order(Importance_ASC$Overall), ]
Importance_ASC$Features_factor <- factor(Importance_ASC$Features, levels = Importance_ASC$Features, ordered = T)
Importance_top10_ASC <- Importance_ASC # [69:78, ]
p_Importance_top10_ASC <- ggplot(Importance_top10_ASC, aes(x = Features_factor, y = Overall, fill = Category))
p_Importance_top10_ASC <- p_Importance_top10_ASC + geom_bar(width = 0.5, stat = "identity") + theme_bw() + 
  coord_flip() + theme_self() + scale_fill_manual(values = c("#E64B35FF", "#00A087FF")) + 
  labs(x = "Features", y = "Importance") + theme(legend.position = 'none')


Importance_CEL$Features <- row.names(Importance_CEL)
Importance_CEL <- Importance_CEL[order(Importance_CEL$Overall), ]
Importance_CEL$Features_factor <- factor(Importance_CEL$Features, levels = Importance_CEL$Features, ordered = T)
Importance_top10_CEL <- Importance_CEL[69:78, ]
p_Importance_top10_CEL <- ggplot(Importance_top10_CEL, aes(x = Features_factor, y = Overall, fill = Category))
p_Importance_top10_CEL <- p_Importance_top10_CEL + geom_bar(width = 0.5, stat = "identity") + theme_bw() + 
  coord_flip() + theme_self() + scale_fill_manual(values = c("#4DBBD5FF", "#E64B35FF", "#00A087FF", "#F39B7FFF")) + 
  labs(x = "Features", y = "Importance") + theme(legend.position = 'none')


Importance_VEN$Features <- row.names(Importance_VEN)
Importance_VEN <- Importance_VEN[order(Importance_VEN$Overall), ]
Importance_VEN$Features_factor <- factor(Importance_VEN$Features, levels = Importance_VEN$Features, ordered = T)
Importance_top10_VEN <- Importance_VEN[69:78, ]
p_Importance_top10_VEN <- ggplot(Importance_top10_VEN, aes(x = Features_factor, y = Overall, fill = Category))
p_Importance_top10_VEN <- p_Importance_top10_VEN + geom_bar(width = 0.5, stat = "identity") + theme_bw() + 
  coord_flip() + theme_self() + scale_fill_manual(values = c("#E64B35FF", "#00A087FF")) + 
  labs(x = "Features", y = "Importance") + theme(legend.position = 'none')

grid.arrange(p_Importance_top10_ASC, p_Importance_top10_CEL, p_Importance_top10_VEN, nrow = 3)

```

## REVISION: Features vs. treatment status 

```{r featurevstreament}
top_10_feature <- Importance[order(-Importance$Overall), ]
top_10_feature <- as.character(top_10_feature[1:10, "Features"])
coreData_Normal_Feature <- coreData_Normal
coreData_Normal_Feature$ENDTRS_C <- core[core$RPT %in% coreData_Normal_Feature$RPT, "ENDTRS_C"]
coreData_Normal_Feature <- coreData_Normal_Feature[, c("new_label", "DISCONT", "ENDTRS_C", top_10_feature)]
coreData_Normal_Feature$new_label <- as.factor(coreData_Normal_Feature$new_label)
coreData_Normal_Feature$ENDTRS_C_NUM <- unlist(lapply(coreData_Normal_Feature$ENDTRS_C, function(x) {
  if (x == "AE") return(3)
  if (x == "possible_AE") return(2)
  if (x == "progression") return(1)
  if (x == "complete") return(0)
}))
coreData_Normal_Feature$new_label <- as.numeric(as.character(coreData_Normal_Feature$new_label))
coreData_Normal_Feature$DISCONT <- as.numeric(as.character(coreData_Normal_Feature$DISCONT))

set.seed(1)
data <- coreData_Normal_Feature
data <- data[sample(nrow(data)), ]
folds <- cut(seq(1, nrow(data)), breaks = 5, labels = F)
cor.df <- as.data.frame(matrix(nrow = 11, ncol = 5))
corSig.df <- as.data.frame(matrix(nrow = 11, ncol = 5))
tests <- data.frame()
for (i in 1:5) {
  testIndexes <- which(folds == i, arr.ind = T)
  test <- data[testIndexes, ]
  train <- data[-testIndexes, ]
  rf.model <- randomForest(new_label ~ ., data = select(train, c(new_label, ALB:MHSOCIAL)))
  pred <- predict(rf.model, select(test, ALB:MHSOCIAL))
  test$rf.model <- pred
  tests <- rbind(tests, test)
}
cors <- lapply(select(tests, ALB:MHSOCIAL, rf.model), cor.test, tests$DISCONT)
cors.estimate <- lapply(cors, `[[`, 'estimate')
cors.significant <- lapply(cors, `[[`, 'p.value')

summary(lm(DISCONT ~ ALB, data = tests))
summary(lm(DISCONT ~ rf.model, data = tests))

tree <- getTree(rf.model, k = 500, labelVar = T) %>% rownames_to_column() %>% 
  mutate(`split point` = ifelse(!is.na(`split var`), `split point`, NA))
graph_frame <- data.frame(from = rep(tree$rowname, 2),
                          to = c(tree$`left daughter`, tree$`right daughter`))
graph <- graph_from_data_frame(graph_frame) %>% delete_vertices("0")
V(graph)$node_label <- as.character(tree$`split var`)
V(graph)$leaf_label <- as.character(round(tree$prediction, 2))
V(graph)$split <- as.character(round(tree$`split point`, digits = 2))
plot <- ggraph(graph, 'dendrogram') + 
    theme_bw() +
    geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = node_label), na.rm = TRUE, repel = TRUE)
#     geom_node_label(aes(label = split), vjust = 2.5, na.rm = TRUE, fill = "white") + 
#     geom_node_label(aes(label = leaf_label, fill = leaf_label), na.rm = TRUE,
# 					repel = TRUE, colour = "white", fontface = "bold", show.legend = FALSE)
```

## MAIN: Final score in DREAM challenge: figure 5

```{r figure5}
res <- read.table("data/q2_results.txt", sep = "\t", header = T, skip = 6, stringsAsFactors = F)
res$team[which(res$team == 'Y G')] <- 'Yuanfang Guan'
res_max <- as_tibble(res) %>%
  group_by(team) %>% filter(AUPRC == max(AUPRC))

res_max <- res_max[!duplicated(res_max$team), ]
res_max <- res_max[order(res_max$AUPRC), ]
res_max$team <- factor(res_max$team, levels = res_max$team)


methods <- as.data.frame(matrix(ncol = 21, nrow = 34))
row.names(methods) <- res_max$team
colnames(methods) <- c("DEATH", "LKADT_P", "DISCONT", "ENDTRS_C", "ENDTRT_PC", "Reconstruction", "Cox", "Random Forest", "Gradient Boosting",
                       "Binomial Regression", "Cluster", "SVM", "Linear Regression", "Neural Network", "Generalized Regression Model",
                       "Elastic Net", "LASSO", "Random Survival Forest", "Logistic Regression", "Ensembl", "Use New Label")

# just type by hand ...  
methods[1, ]  <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[2, ]  <- 2
methods[3, ]  <- 2
methods[4, ]  <- c(0, 0, 1, 0, 1, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[5, ]  <- c(2, 2, 2, 2, 2, 2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[6, ]  <- 2
methods[7, ]  <- c(0, 0, 1, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0)
methods[8, ]  <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[9, ]  <- c(0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 1, 0)
methods[10, ] <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[11, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[12, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 0, 0, 1, 0)
methods[13, ] <- 2
methods[14, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0)
methods[15, ] <- c(1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0)
methods[16, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 1, 0)
methods[17, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 1, 1, 0)
methods[18, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[19, ] <- 2
methods[20, ] <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1)
methods[21, ] <- c(0, 0, 1, 0, 1, 1, 0, 1, 1, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0)
methods[22, ] <- c(0, 0, 1, 0, 1, 0, 1, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 1, 0)
methods[23, ] <- c(0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 1)
methods[24, ] <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[25, ] <- c(0, 0, 1, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0)
methods[26, ] <- c(0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[27, ] <- 2
methods[28, ] <- c(0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0)
methods[29, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0)
methods[30, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[31, ] <- c(0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0)
methods[32, ] <- c(0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[33, ] <- c(0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
methods[34, ] <- c(1, 1, 1, 1, 1, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1)

methods <- as_tibble(methods)
res_all <- bind_cols(res_max, methods)
res_all <- gather(res_all, Class, labels, DEATH:`Use New Label`) %>%
  mutate(Group = ifelse(Class %in% c("DEATH", "LKADT_P", "DISCONT", "ENDTRS_C", "ENDTRT_PC", "Reconstruction"), "Gold Standard\nConstruction", "Model/Strategy"))
res_all$labels <- as.factor(res_all$labels)
res_all$Group <- as.factor(res_all$Group)

# A
p0 <- ggplot(res_all)
p0 <- p0 + geom_tile(aes(x = team, y = Class, fill = labels), color = "black") + coord_flip() + theme_self() +
  theme(legend.position = "none", axis.ticks = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), axis.title.x = element_blank(), axis.line = element_blank(), panel.border = element_blank()) + scale_fill_manual(values = c("White", "#0073C2FF", "#868686FF")) + facet_grid(~Group, space="free", scale="free") + labs(x = 'Teams')
p0

p <- ggplot(res_max)
p <- p + geom_bar(aes(x = team, y = AUPRC), stat = "identity", fill = "#DF8F44FF") + geom_hline(yintercept = 0.104, linetype = "dashed") +
  coord_flip() + theme_self() + scale_fill_aaas() + 
  theme(legend.position = c(0.8, 0.05), legend.title = element_blank(), panel.border = element_blank(), 
        axis.text.y = element_blank(), axis.ticks = element_blank(), axis.line.x = element_line(size = 0.5)) + 
  geom_text(aes(x = team, y = AUPRC, label = round(AUPRC, 4)), hjust = 1, nudge_x = 0.05, color = 'black') + 
  labs(x = '', y = 'Area Under PR Curve')
p

# B
p1 <- ggplot(res_max[27:34, ]) + 
  geom_bar(aes(x = team, y = p.val_random), fill = '#79AF97FF', size = 3, stat = "identity") + 
  theme_self() + coord_flip() + 
  labs(x = '', y = 'p-Value') + 
  geom_text(aes(x = team, y = p.val_random, label = round(p.val_random, 3)), hjust = 1)
p1

# C
p2 <- ggplot(res_max[27:34, ]) + 
  geom_bar(aes(x = team, y = Bayes_factor), fill = '#00A1D5FF', size = 3, stat = "identity") + 
  theme_self() + coord_flip() + 
  geom_text(aes(x = team, y = Bayes_factor, label = round(Bayes_factor, 2)), hjust = 1) + 
  labs(x = '', y = 'Bayes Factor')
p2
```

## MAIN: Proportion of missing values: figure S1

```{r figureS1}
core[core == ""] <- NA
core[core == "."] <- NA
missing_table <- colMeans(is.na(core[, 12:131]))
missing_table <- data.frame(feature = names(missing_table), prop = missing_table, stringsAsFactors = F)
missing_table <- missing_table[order(-missing_table$prop), ]
missing_table$feature <- factor(missing_table$feature, levels = missing_table$feature, ordered = T)
ggplot(missing_table, aes(x = feature, y = prop)) + geom_bar(stat = "identity", fill = "#91D1C2FF") + scale_y_continuous(limits = c(0, 1)) + 
  theme_self() + 
  labs(x = "Features", y = "Missing proportion") + coord_flip()
```

## MAIN: t-SNE: figure S2

```{r figureS2}
# The shape of figure will change every time when you run the code 
# but the pattern of cohort effects will keep the same
RPT <- unlist(lapply(strsplit(coreData_Normal$RPT, split = "-"), "[", 1))
RPT <- as.factor(RPT)
color <- c("#FF410DFF", "#D0DFE6FF", "#95CC5EFF")

names(color) <- unique(RPT)
tsne <- Rtsne(coreData_Normal[, c(7:84)])
tsne_frame <- as.data.frame(tsne$Y)
tsne_frame$cohort <- RPT
p_tsne <- ggplot(tsne_frame, aes(x = V1, y = V2, color = cohort))
p_tsne <- p_tsne + geom_point() + theme_bw() + theme(panel.background = element_blank(), panel.grid = element_blank()) + 
  labs(x = "t-SNE Variable 1", y = "t-SNE Variable 2") + scale_color_manual(values = color, labels = c("ASC", "CEL", "VEN")) + theme_self()
```